---
title: "Análise Exploratório de Dados (EDA)"
date: "Junho de 2020"
---

```{r setup_exploration, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.pos =  "h")
knitr::opts_knit$set(root.dir = "../")

# loading required libraries
library(rmarkdown)
library(dplyr)
library(readr)
library(rgdal)
library(readxl)
library(forcats)
library(ggplot2)
library(ggthemes)
library(ggpubr)
library(ggalluvial)
library(tidyr)
library(lubridate)
library(stringr)
library(VIM)
library(psych)
library(feather)
library(tinytex)
library(knitr)
library(leaflet)
library(geojsonio)
```

```{r scripts_exploration, include=FALSE}
# loading required steps before performing the analysis
source("./src/util/auxiliary_functions.R")
source("./src/datapreparation/step_07_data_load.R")
```

# Exploration 1

Describe your exploration 1 here, including some plots, tables or any resource used.

```{r exploration_target_1, echo=TRUE, out.width = '100%', fig.height = 6}
ggplot(data = gas_prices_station) +
  geom_boxplot(aes(y = PcVenda, 
                   x = fct_reorder(Cidade, PcVenda, .desc = FALSE),
                   fill = Estado), 
               show.legend = FALSE
               ) +
  coord_flip() +
  labs(title = 'Preço de Gasolina Comum por Estado',
       subtitle = 'Semana de 2020-04-26 a 2020-05-02',
       x = 'Estado',
       y = 'Preço') + 
  theme(panel.grid = element_blank(),
        aspect.ratio = 1.2)
```

# Exploration 2

Describe your exploration 2 here, including some plots, tables or any resource used.

```{r exploration_target_2, echo=TRUE, out.width = '100%'}
# your code with the exploration 2 goes here
```


# Exploration 3

Describe your exploration 3 here, including some plots, tables or any resource used.

```{r exploration_target_3, echo=TRUE, out.width = '100%'}
# your code with the exploration 3 goes here
```

# Exploration n

Describe your exploration n here, including some plots, tables or any resource used.

```{r exploration_target_n, echo=TRUE, out.width = '100%'}
# your code with the exploration n goes here
```
